Supplement to Example Manuscript Template for a Data Analysis Project

### 2024-08-06 products/manuscript/supplement/Supplementary-Material.qmd
fix graph in supplement material

# Additional results
## Log-Transformed Histogram Examples
![Individual Retirement Payments](../../../results/figures/scatterplots/Individual%20retirement%20arrangement%20payments%20amount_scatterplot.png)

>>>>

# Additional results
## Log-Transformed Histogram Examples
![Individual Retirement Payments](../../../results/figures/histograms/Individual%20retirement%20arrangement%20payments%20amount_histogram.png)
